---
title: #Tabula Assignment
#April 16, 2019
#Advanced Reporting, School of Journalism
#Brooke Tomlin 
output: html_document
---
```{r}
library(tidyverse)
library(rio)
library(janitor)
library(formattable)
```

```{r}
x <- rio::import ("https://docs.google.com/spreadsheets/d/1u1w4Xd28Kp7v5BeKNmhNkjU3eRmt-uzzm5YKd70Y4Ms/edit#gid=1292931470")
```


```{r}
UA2015_19 <- as.data.frame(t(x))
```

```{r}
UA2015_19 <- UA2015_19 %>%
  row_to_names(row_number = 1)
UA2015_19
```

```{r}
colnames(UA2015_19)[1] <- "Year"
UA2015_19[1:4] <- lapply(UA2015_19[1:4], as.character)
glimpse(UA2015_19)
```

```{r}
library(janitor)
UA2015_19 <- janitor::clean_names(UA2015_19)
head(UA2015_19)
```

```{r}
UA2015_19$in_state <- as.numeric(gsub(",", "", UA2015_19$in_state))
UA2015_19$out_of_state <- as.numeric(gsub(",", "", UA2015_19$out_of_state))
UA2015_19$international <- as.numeric(gsub(",", "", UA2015_19$international))
UA2015_19
```


```{r}
UA2015_19 <- UA2015_19 %>%
  mutate(pct_chg = (in_state/lag(in_state)-1))
UA2015_19
```

```{r}
UA2015_19 <- UA2015_19 %>%
  mutate(total = in_state + out_of_state + international)
UA2015_19
```

```{r}
#Format into percents
UA2015_19$pct_chg <- percent(UA2015_19$pct_chg)
```

```{r}
UA2015_19 %>% 
  ggplot(aes(x = year, y = pct_chg, fill = pct_chg)) +
  geom_col(position = "dodge", show.legend = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_text(aes(label = pct_chg), hjust = -.5, size = 2) +
  #scale_y_continuous(limits=c(0, .10),labels = scales::percent) +
  coord_flip() +
  labs(title = "Percent Change in UofA Enrollment, 2015-2019",
       subtitle = "U of A Enrollment",
       caption = "Graphic by Brooke Tomlin, 4-16-2020",
       y="Source: UA Annual Report",
       x="")
UA2015_19
```

```{r}
#Import Zillow Data
Zillow <- rio::import('https://docs.google.com/spreadsheets/d/1l_kzd_BN_F-kI3c3p3_VB3mdqYxRWADvIxOiBsj93GQ/edit#gid=819464580')
```

```{r}
ZillowFay <- Zillow %>% filter(RegionName == "Fayetteville, AR")
head(ZillowFay)
```


```{r}
# Number columns
ncol(ZillowFay)
```

```{r}
# Number rows
nrow(ZillowFay)
```
```{r}
#check data types
glimpse(ZillowFay)
```

```{r}
#Clean Headers - Janitor package
#install.packages("janitor")
library(janitor)
ZillowFay <- janitor::clean_names(ZillowFay)
head(ZillowFay)
```

```{r}
#Run stats on latest January 2020 data
summary(ZillowFay$x2020_01)
```   

### Percent Change, 9/2010 to 1/2020

```{r}
ZillowP <- ZillowFay %>%
  mutate(Total_pct_change = (x2010_09/lag(x2010_09)-1))
```

```{r}
Z_AR_PCT <- ZillowFay %>% 
  select(region_name, x2010_09, x2020_01) %>% 
  mutate(Pct_Chg=((x2020_01-x2010_09)/(x2010_09))) 
Z_AR_PCT
```


```{r}
#To quickly format into percents, load
#install.packages("formattable")
library(formattable)
#
Z_AR_PCT$Pct_Chg <- percent(Z_AR_PCT$Pct_Chg)
Z_AR_PCT
```
```

```{r}
#Do some math - average value for Arkansas Sept 2010
avg2010 <- mean(Z_AR_PCT$x2010_09, na.rm=TRUE)
avg2010
#Average value for Fayetteville, Sept. 2010= 875
```

```{r}
#Do some math - average value for Arkansas Nov 2019
avg2020 <- mean(Z_AR_PCT$x2020_01, na.rm=TRUE)
avg2020
#Average value for Fayetteville, Jan. 2020= 1074
```

```{r}
avg <- ((avg2020-avg2010)/avg2010)*100

avg <- round(avg, 2)
#22.74
avg
```

### Chart Data

```{r}
Z_AR_PCT %>% 
  filter(Pct_Chg > .20) %>% 
  ggplot(aes(x = reorder(region_name, Pct_Chg), y = Pct_Chg, fill = Pct_Chg)) +
geom_col(position = "dodge", show.legend = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_text(aes(label = Pct_Chg), hjust = -.5, size = 2) +
  scale_y_continuous(limits=c(0, .45),labels = scales::percent) +
  coord_flip() +
  labs(title = "Fayetteville Real Estate Values, 2010-2020",
       subtitle = "Statewide Average: 22.74% Increase. ",
       caption = "Graphic by Brooke Tomlin, 4-16-2020",
       y="Source: Zillow Housing Index",
       x="")
```
